% !TeX root = ../main.tex

\uestcsetup{
  keywords  = {学位论文, 撰写规范, 论文模板, 电子科技大学},
  keywords* = {Dissertation/Thesis, Writing Specification, Thesis Template, University of Electronic Science and Technology of China},
}

\begin{abstract}
  为进一步规范我校研究生学位论文撰写格式，提高研究生学位论文质量，参照国家标准《学位论文编写规则》（GB/T 7713.1-2006），结合我校实际，制定本规范。

  本次修订相对于上一版（2016版）的主要变化如下。

  \begin{enumerate}
    \item 按照规范要求重新编写文档，预置主要格式样式，可作为论文模板使用。
    \item 更新封面、扉页等固定页面模板，并增加填写说明。
    \item 更新摘要、绪论、正文、结论撰写说明，以及全文语言、表述注意事项。
    \item 参照最新国家标准，调整参考文献格式要求。
    \item 明确部分格式要求细节，例如表格的三线表样式，图表附注的格式。
    \item 调整部分格式要求细节，例如超过一行的图题、表题取消悬挂缩进对齐。
    \item 附录增加学院、学术学位学科、专业学位类别的中、英文名称对照表。
  \end{enumerate}

  本文档可在研究生院网站下载，网址：https://gr.uestc.edu.cn。如有变动，以研究生院网站最新公布的版本为准。
\end{abstract}

\begin{abstract*}
  In order to further standardize the format of dissertation/thesis writing and improve graduate dissertation/thesis quality, this specification is formulated with reference to the national standard "Rules for Dissertation Writing" (GB/T 7713.1-2006) and the reality of UESTC.

  The main changes in this revision from the last version (Ver. 2016) are as follows.

  \begin{enumerate}
    \item Rewrite the document according to the requirements of the specifications, and preset main formatting styles, which makes it more suitable for use as a template.
    \item Update fixed page templates such as cover page and title page, and add filling instructions.
    \item Update the writing instructions of abstract, introduction, main chapters, and conclusions, as well as the notes on language and presentation.
    \item Adjust reference format requirements with reference to latest national standards.
    \item Clarify some details of format requirements, e.g., three-line style for tables, format for figure/table annotations.
    \item Adjust some details of format requirements, e.g., cancel hanging indent for figure/table titles consisting of 2 or more lines of texts.
    \item Add comparison tables of Chinese and English names of colleges, academic degree disciplines, and professional degree categories in Appendixes.
  \end{enumerate}

  This document can be downloaded from the Graduate School website at https://gr.uestc.edu.cn. In case of any changes, the latest version published on the Graduate School website shall prevail.

\end{abstract*}
